Testing atlantisom: true biomass output from Atlantis

### 2019-04-26 TrueBioTest.Rmd
rearrange setup again

First, you will want to install atlantisom if you haven't already.

@@

Next, load packages.

```{r message=FALSE, warning=FALSE}
library(tidyr)
require(dplyr)
library(ggplot2)
library(data.table)
library(here)
library(atlantisom)
```

>>>>

First, you will want to set up libraries and install atlantisom if you haven't already.

```{r message=FALSE, warning=FALSE}
library(tidyr)
require(dplyr)
library(ggplot2)
library(data.table)
library(here)
```

@@

Next, load the package.

```{r message=FALSE, warning=FALSE}
library(atlantisom)
```
